High-level statistical overview: 
    End point of this simulation is a set of structural equation models aka SEMs, which are in practice connecting sets of many variable's
    associations with each other. And in the context of field ecology, a lot of 
    things such as linear mixed models are utilized.

Experimental design:
    10 study sites, which each have a control and treatment location, likely 
    with 5 days of surveying at each site. Bees are sampled for both their
    abundance and species composition. Sites need to be at least 500m apart from
    one another based on current research precedence (Fitch et al 2021).
    Sampling must occur at specific appropriate weather conditions, from 09:00
    to 17:30, within a temperature range of 20 to 35°C, some amount of sun and
    wind speeds not over 4 m/s (Brown et al, 2024). These conditions of sampling
    are meant to provide appropriate timing for bees to be present, which are
    then used for measuring abundance and Shannon-diversity index data (Ferrari
    et al, 2022).
    Separately, plant diversity can be measured with Shannon index as well, for
    plant abundance it is more complicated but a very readily available species
    can be utilized instead, ie Trifolium pratense L. (Hennig et al, 2011).
    These sites are specifically roadsides, which creates additional variables
    of road width (Fitch et al, 2021), noise pollution and more physical
    contaminants from cars ie metals are added factors (Phillips et al, 2021).
    There is also excess salt usage to factor in areas such as the study site of
    Toronto, where road salt used from the winter will inevitably seep into
    roadside soil (Caplan et al, 2024).
    Lastly, water runoff is a variable which is to be sampled and studied as
    well, but I am still undecided if this should be a dataset only looking at
    the volume of water in runoff, or contents (pollution) of urban runoff water
    (Zhange et al, 2010).

Lower-level statistical overview:
    Two separate structural equation models. One has bee abundance as the           endogenous aka dependent variable at top of heirarchy, with plant abundance
    (specifically that of Trifolium pratense L.), noise pollution and road width
    as its exogenous aka independent variables. But Trifolium abundance
    separately has its own independent variables, in this case soil 
    contamination. In practice, using Trifolium as the only plant species here
    changes how impactful soil pollution effects are based on what pollutants
    in particular affect that species (Shahbaz et al, 2018) and their functional
    group. The point is, this particular SEM is not what I would be practically
    applying. There are some things here and there that could be swapped, but
    this is more for demonstrative purposes.
    The other SEM is bee Shannon index diversity as top dependent variable, then
    plant Shannon diversity, noise pollution and road width as its independent
    variables. Soil contamination is plant Shannon diversity's exogenous
    variable.
    I will be assuming normal distribution for all variables present in the
    context of this simulation, and linear mixed models will be utilized as this
    is not an ideal/optimal data set, there are practical restrictions such as
    which residential site owners are ok with fieldwork occuring at their
    property, mowing schedule of the city for public sites etc.
    
Version info:
    R version 4.3.3
    Packages:
        ggplot version 3.5.1
        languageserver version 0.3.16
        lavaan version 0.6-19
        lisrelToR version 0.3
        MplusAutomation version 1.1.
        OpenMx version 2.21.1
        sem version 3.1-15
        semPlot version 1.1.6

Packages:
```{r}
load("languageserver")
load("lavaan")
load("lisrelToR")
load("MplusAutomation")
load("OpenMx")
load("sem")
load("semPlot")
```

Simulating data sets:
```{r}

```
    
Citations:
Brown, J., Threlfall, C. G., Harrison, L., Baumann, J., & Williams, N. S. (2024). Rapid responses of bees and butterflies but not birds to targeted urban road verge habitat enhancements. Journal of Applied Ecology.
Caplan, J. S., Salisbury, A. B., McKenzie, E. R., Behbahani, A., & Eisenman, S. W. (2024). Spatial, temporal, and biological factors influencing plant responses to deicing salt in roadside bioinfiltration basins. Journal of Environmental Management, 359, 120761.
Ferrari, A., & Polidori, C. (2022). How city traits affect taxonomic and functional diversity of urban wild bee communities: insights from a worldwide analysis. Apidologie, 53(4), 46.
Fitch, G., & Vaidya, C. (2021). Roads pose a significant barrier to bee movement, mediated by road size, traffic and bee identity. Journal of Applied Ecology, 58(6), 1177-1186.
Hennig, E. I., & Ghazoul, J. (2011). Plant–pollinator interactions within the urban environment. Perspectives in Plant Ecology, Evolution and Systematics, 13(2), 137-150.
Phillips, B. B., Bullock, J. M., Gaston, K. J., Hudson‐Edwards, K. A., Bamford, M., Cruse, D., ... & Osborne, J. L. (2021). Impacts of multiple pollutants on pollinator activity in road verges. Journal of Applied Ecology, 58(5), 1017-1029.
Shahbaz, A. K., Iqbal, M., Jabbar, A., Hussain, S., & Ibrahim, M. (2018). Assessment of nickel bioavailability through chemical extractants and red clover (Trifolium pratense L.) in an amended soil: Related changes in various parameters of red clover. Ecotoxicology and Environmental Safety, 149, 116-127.
Zhang, M., Chen, H., Wang, J., & Pan, G. (2010). Rainwater utilization and storm pollution control based on urban runoff characterization. Journal of Environmental Sciences, 22(1), 40-46.