High-level statistical overview: 
    End point of this simulation is a set of structural equation models aka SEMs
    , which are in practice connecting sets of many variable's associations with 
    each other. And in the context of field ecology, a lot of things such as 
    linear mixed models are utilized.

Experimental design:
    10 study sites, which each have a control and treatment location, likely 
    with 5 days of surveying at each site. Bees are sampled for both their
    abundance and species composition. Sites need to be at least 500m apart from
    one another based on current research precedence (Fitch et al 2021).
    Sampling must occur at specific appropriate weather conditions, from 09:00
    to 17:30, within a temperature range of 20 to 35°C, some amount of sun and
    wind speeds not over 4 m/s (Brown et al, 2024). These conditions of sampling
    are meant to provide appropriate timing for bees to be present, which are
    then used for measuring abundance and Shannon-diversity index data (Ferrari
    et al, 2022).
    Separately, plant diversity is measured. For plant abundance it is more 
    complicated but a very readily available species can be utilized instead, ie
    Trifolium pratense L. (Hennig et al, 2011). For the purposes of this
    simulation, bee and plant abundance will be ignored, but eventually they
    will be a factor.
    These sites are specifically roadsides, which creates additional variables
    of road width (Fitch et al, 2021), noise pollution and more physical
    contaminants from cars ie metals are added factors (Phillips et al, 2021).
    There is also excess salt usage to factor in areas such as the study site of
    Toronto, where road salt used from the winter will inevitably seep into
    roadside soil (Caplan et al, 2024).
    Lastly, water runoff is a variable which is to be sampled and studied as
    well, but I am still undecided if this should be a dataset only looking at
    the volume of water in runoff, or contents (pollution) of urban runoff water
    (Zhange et al, 2010).

Lower-level statistical overview:
    The SEM is bee diversity as top endogenous aka dependent variable, then
    plant diversity, noise pollution and road width as its exogenous aka 
    independent variables. Soil contamination is plant diversity's independent
    variable.
    I will be assuming normal distribution for all variables present in the
    context of this simulation, and linear mixed models will be utilized as this
    is not an ideal/optimal data set, there are practical restrictions such as
    which residential site owners are ok with fieldwork occuring at their
    property, mowing schedule of the city for public sites etc. Likewise the
    Shannon index data will not be included for the purposes of this simulation
    as abundance values need to be included, which is still a work in process
    and importantly no current research precedence of utilizing Shannon
    diversity indexes for this specific study design (urban roadside
    pollination).
    
Version info:
    R version 4.3.3
    Packages:
        emmeans version 1.10.5
        ggplot2 version 3.5.1
        languageserver version 0.3.16
        lavaan version 0.6-19
        lisrelToR version 0.3
        lme4 version 1.1-31
        matrix version 1.5-3
        MplusAutomation version 1.1.1
        mvtnorm version 1.3-1
        OpenMx version 2.21.1
        sem version 3.1-15
        semPlot version 1.1.6
        tidyverse version 2.0.0

Packages:
```{r}
load(emmeans)
load(ggplot2)
load(languageserver)
load(lavaan)
load(lisrelToR)
load(lme4)
load(matrix)
load(MplusAutomation)
load(mvtnorm)
load(OpenMx)
load(sem)
load(semPlot)
load(tidyverse)
```
Simulating starting data:
```{r}
set.seed(42)

# Create base data frame with site and treatment information
sites_df <- expand.grid(
  site = 1:10,
  day = 1:5,
  treatment = c("Treatment", "Control")
)

# Pairing normal data
generate_paired_data <- function(treatment_mean, control_mean, treatment_sd, control_sd, n) {
  treatment_values <- pmax(0, rnorm(n, treatment_mean, treatment_sd))
  control_values <- pmax(0, rnorm(n, control_mean, control_sd))
  c(rbind(treatment_values, control_values))
}

# Generate data
df <- sites_df %>%
  arrange(site, day) %>%
  mutate(
    # Bee diversity (separate for treatment and control)
    bee_diversity = generate_paired_data(100, 20, 10, 5, 50),
    
    # Plant diversity (separate for treatment and control)
    plant_diversity = generate_paired_data(12, 3, 2, 1, 50),
    
    # Road width (same for treatment and control at each site)
    road_width = rep(rep(rnorm(10, 17, 2), each = 2), 5),
    
    # Noise pollution (varying by day and site)
    noise_pollution = rep(rnorm(100, 62.9, 5), 1),
    
    # Salt pollution (same for treatment and control at each site)
    salt_pollution = rep(rep(rnorm(10, 1, 100), each = 2), 5)
  )
```

Plotting linear mixed models:
```{r}
# Create the plots with fixed aesthetics
# 1. Bee diversity vs. plant diversity
p1 <- ggplot(df, aes(x = plant_diversity, y = bee_diversity, color = treatment)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE) +
  scale_color_manual(values = c("Control" = "#4F7F7F", "Treatment" = "#800000")) +
  labs(
    title = "Bee Diversity vs. Plant Diversity",
    x = "Plant Diversity (species count)",
    y = "Bee Diversity (species count)",
    color = "Treatment"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )

# 2. Bee diversity vs. noise pollution
p2 <- ggplot(df, aes(x = noise_pollution, y = bee_diversity, color = treatment)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE) +
  scale_color_manual(values = c("Control" = "#4F7F7F", "Treatment" = "#800000")) +
  labs(
    title = "Bee Diversity vs. Noise Pollution",
    x = "Noise Pollution (dBA)",
    y = "Bee Diversity (species count)",
    color = "Treatment"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )

# 3. Bee diversity vs. road width
p3 <- ggplot(df, aes(x = road_width, y = bee_diversity, color = treatment)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE) +
  scale_color_manual(values = c("Control" = "#4F7F7F", "Treatment" = "#800000")) +
  labs(
    title = "Bee Diversity vs. Road Width",
    x = "Road Width (meters)",
    y = "Bee Diversity (species count)",
    color = "Treatment"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )

# 4. Plant diversity vs. salt pollution
p4 <- ggplot(df, aes(x = salt_pollution, y = plant_diversity, color = treatment)) +
  geom_point(alpha = 0.6, size = 3) +
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE) +
  scale_color_manual(values = c("Control" = "#4F7F7F", "Treatment" = "#800000")) +
  labs(
    title = "Plant Diversity vs. Salt Pollution",
    x = "Salt Pollution (mg/g)",
    y = "Plant Diversity (species count)",
    color = "Treatment"
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12)
  )

# Display plots
print(p1)
print(p2)
print(p3)
print(p4)
```

Structural equation model data:
```{r}
# First, let's look at the correlation structure
df_agg <- df %>%
  group_by(site, treatment) %>%
  summarize(
    bee_diversity = mean(bee_diversity),
    plant_diversity = mean(plant_diversity),
    road_width = mean(road_width),
    noise_pollution = mean(noise_pollution),
    salt_pollution = mean(salt_pollution),
    .groups = 'drop'
  )

# Check correlation matrices for each group
cor_treatment <- df_agg %>%
  filter(treatment == "Treatment") %>%
  select(-treatment, -site) %>%
  cor()
print("Correlation matrix - Treatment group:")
print(round(cor_treatment, 3))

cor_control <- df_agg %>%
  filter(treatment == "Control") %>%
  select(-treatment, -site) %>%
  cor()
print("Correlation matrix - Control group:")
print(round(cor_control, 3))

# Let's try a simplified model structure
# We'll analyze treatment and control groups separately
# and remove covariances between exogenous variables

model_simple <- '
  # Direct effects on bee diversity
  bee_diversity ~ plant_diversity + road_width + noise_pollution
  
  # Effect on plant diversity
  plant_diversity ~ salt_pollution
'

# Fit separate models for each group
df_treatment <- df_agg %>% filter(treatment == "Treatment")
df_control <- df_agg %>% filter(treatment == "Control")

# Try to fit treatment model
fit_treatment <- try(sem(model_simple, 
                        data = df_treatment,
                        estimator = "MLM"))

# Try to fit control model
fit_control <- try(sem(model_simple, 
                      data = df_control,
                      estimator = "MLM"))

# Function to safely extract and format results
safe_extract_results <- function(fit, group_name) {
  if (inherits(fit, "try-error")) {
    return(data.frame(
      Group = group_name,
      Path = "Model failed to converge",
      Estimate = NA,
      P_value = NA
    ))
  }
  
  params <- standardizedSolution(fit)
  params <- params[params$op == "~", ]
  data.frame(
    Group = group_name,
    Path = paste(params$lhs, "<-", params$rhs),
    Estimate = round(params$est.std, 3),
    P_value = round(params$pvalue, 3)
  )
}

# Extract results if models converged
results_treatment <- safe_extract_results(fit_treatment, "Treatment")
results_control <- safe_extract_results(fit_control, "Control")

# Combine and print results
results <- rbind(results_treatment, results_control)
print(results)

# Alternative approach: Path analysis using individual regressions
path_analysis <- function(data) {
  # Model 1: Plant diversity ~ Salt pollution
  m1 <- lm(plant_diversity ~ salt_pollution, data = data)
  
  # Model 2: Bee diversity ~ All predictors
  m2 <- lm(bee_diversity ~ plant_diversity + road_width + noise_pollution, 
           data = data)
  
  # Extract and format results
  m1_coef <- summary(m1)$coefficients
  m2_coef <- summary(m2)$coefficients
  
  results <- data.frame(
    Path = c("plant_diversity ~ salt_pollution",
             "bee_diversity ~ plant_diversity",
             "bee_diversity ~ road_width",
             "bee_diversity ~ noise_pollution"),
    Estimate = c(coef(m1)[2], coef(m2)[2:4]),
    Std_Error = c(m1_coef[2,2], m2_coef[2:4,2]),
    P_value = c(m1_coef[2,4], m2_coef[2:4,4])
  )
  
  return(results)
}

# Run path analysis for each group
path_results_treatment <- path_analysis(df_treatment)
path_results_treatment$Group <- "Treatment"

path_results_control <- path_analysis(df_control)
path_results_control$Group <- "Control"

# Combine and print path analysis results
path_results <- rbind(path_results_treatment, path_results_control)
print("Path Analysis Results:")
print(path_results)

```

Citations:
Brown, J., Threlfall, C. G., Harrison, L., Baumann, J., & Williams, N. S. (2024). Rapid responses of bees and butterflies but not birds to targeted urban road verge habitat enhancements. Journal of Applied Ecology.
Caplan, J. S., Salisbury, A. B., McKenzie, E. R., Behbahani, A., & Eisenman, S. W. (2024). Spatial, temporal, and biological factors influencing plant responses to deicing salt in roadside bioinfiltration basins. Journal of Environmental Management, 359, 120761.
Ferrari, A., & Polidori, C. (2022). How city traits affect taxonomic and functional diversity of urban wild bee communities: insights from a worldwide analysis. Apidologie, 53(4), 46.
Fitch, G., & Vaidya, C. (2021). Roads pose a significant barrier to bee movement, mediated by road size, traffic and bee identity. Journal of Applied Ecology, 58(6), 1177-1186.
Hennig, E. I., & Ghazoul, J. (2011). Plant–pollinator interactions within the urban environment. Perspectives in Plant Ecology, Evolution and Systematics, 13(2), 137-150.
Oiamo, T. H., Davies, H., Rainham, D., & Rinner, C. (2017). Environmental Noise Study in the City of Toronto. City of Toronto Public Health Project: Toronto, ON, Canada.
Phillips, B. B., Bullock, J. M., Gaston, K. J., Hudson‐Edwards, K. A., Bamford, M., Cruse, D., ... & Osborne, J. L. (2021). Impacts of multiple pollutants on pollinator activity in road verges. Journal of Applied Ecology, 58(5), 1017-1029.
Shahbaz, A. K., Iqbal, M., Jabbar, A., Hussain, S., & Ibrahim, M. (2018). Assessment of nickel bioavailability through chemical extractants and red clover (Trifolium pratense L.) in an amended soil: Related changes in various parameters of red clover. Ecotoxicology and Environmental Safety, 149, 116-127.
Zhang, M., Chen, H., Wang, J., & Pan, G. (2010). Rainwater utilization and storm pollution control based on urban runoff characterization. Journal of Environmental Sciences, 22(1), 40-46.